### 2024-10-08 exposeBerlin2410/exposeBerlin2410.tex
presentation Berlin

\vspace{.2cm}
\centerline{\includegraphics[scale=1.7]{wigglyFlipGraph}\quad\includegraphics[scale=1.7]{wigglyLattice}}

\vspace{.3cm}

DMG Seminar Berlin --- October 9, 2024

@@

@@

\vspace{.5cm}
\centerline{\includegraphics[scale=3]{bijection}}

@@

\theo{QU 1a}{Is the wiggly flip graph Hamiltonian?

@@

\theo{QU 1b}{What is the diameter of the wiggly flip graph?

@@

\begin{slide}{Open problem 2: wiggly pseudotriangulations of point sets}

@@

\vspace*{-15cm}
\begin{minipage}{13cm}
\theo{Q2a}{Is~$\wigglyComplex_{\b{P}}$ the boundary complex of a simplicial polytope?

@@

\vspace{1cm}
\theo{Q2b}{Is the graph of~$\wigglyComplex_{\b{P}}$ Hamiltonian?}

@@

>>>>

\vspace{-.2cm}
\centerline{\includegraphics[scale=1.8]{wigglyFlipGraph}\quad\raisebox{.5cm}{\includegraphics[scale=1.8]{wigglyLattice}}}

\vspace{.1cm}
DMG Seminar Berlin --- October 9, 2024

@@

\begin{slide}{Three geometric structures}

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures0}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\bigskip
\begin{center}
\begin{tabular}{rl}
\emph{triangulation} & = maximal crossing-free set of edges \\
\vspace{.3cm}
\\

\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
\vspace{.3cm}
\\

\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
\\
\end{tabular}
\end{center}
\end{slide}

\begin{slide}{Three geometric structures}

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures1}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\bigskip
\begin{center}
\begin{tabular}{rl}
\emph{triangulation} & = maximal crossing-free set of edges \\
\vspace{.3cm}
\\

\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
\vspace{.3cm}
\\

\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
\\
\end{tabular}
\end{center}
\end{slide}

\begin{slide}{Three geometric structures}

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures2}\end{center}
\vspace{-1.08cm} \hspace*{25.7cm} ${k=2}$

\bigskip
\begin{center}
\begin{tabular}{rl}
\emph{triangulation} & = maximal crossing-free set of edges \\
\vspace{.3cm}
& = decomposition into triangles \\

\emph{pseudotriangulation} & = maximal crossing-free pointed set of edges \\
\vspace{.3cm}
& = decomposition into pseudotriangles \\

\emph{$k$-triangulation} & = maximal $(k+1)$-crossing-free set of edges \\
& = decomposition into $k$-stars
\end{tabular}
\end{center}

\vspace{.2cm}
\papier{VP \& F. Santos, Multitriangulations as complexes of star polygons, 2009.}

\vspace{-1cm}
\end{slide}

\begin{slide}{Three geometric structures}

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\begin{center}\includegraphics[scale=1.9]{geometricStructures3}\end{center}
\vspace{-8cm} \hspace*{25.7cm} ${k=2}$

\vspace{7cm}
\begin{center}
\emph{flip} = exchange an internal edge with the common bisector of the two adjacent cells
\end{center}

\vspace{-1cm}
\end{slide}

\begin{slide}{Three geometric structures}

\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
\begin{center}
\begin{tabular}{r@{\quad $\longleftrightarrow$ \quad}l}
\emph{associahedron} & crossing-free sets of internal edges \\
\emph{pseudotriangulations polytope} & pointed crossing-free sets of internal edges \\
{\red multiassociahedron} & $(k+1)$-crossing-free sets of $k$-internal edges
\end{tabular}
\end{center}

\vspace{-1cm}
\end{slide}

%\begin{slide}{Three geometric structures}
%\vspace{-.8cm}
%\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations
%\begin{center}\includegraphics[width=.95\textwidth]{geometricStructures4}\hspace*{1.5cm}~\end{center}
%
%\vspace{-.7cm}
%\begin{flushright}
%``Our main limits in understanding the combinatorial structure of polytopes still\\
%lie in our ability to raise the good questions and in the \emph{lack of examples},\\
%\emph{methods of constructing them}, and \emph{means of classifying them}.'' \\
%\papier{G. Kalai, \emph{Handbook of Discrete \& Computational Geometry}.}
%\end{flushright}
%
%\vspace{-2cm}
%\end{slide}

%%%%%%%

\begin{slide}{LINE SPACE OF THE PLANE = M\"OBIUS STRIP}

\centerline{\includegraphics[angle=-90,scale=2]{MoebiusBand}}

%%%%%%%

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5\n}\\
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures5}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures6}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}

\multido{\n=0+1}{10}{%
\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7\n}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$
\end{slide}
}

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
\vspace{-.5cm}\\
\vspace*{-2cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7}
\vspace{-8.5cm} \\ \hspace*{25.7cm} ${k=2}$

\vspace{7.6cm}
\papier{VP \& M. Pocchiola, Multitriangulations, pseudotriangulations and primitive sorting networks, 2012.}

\vspace*{-3cm}
\end{slide}

%%%%%%%%%

\begin{slide}{Duality}
\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations

\vspace{1.3cm}
\begin{center}\includegraphics[scale=1.9]{geometricStructures8}\end{center}
\vspace{-8.33cm} \hspace*{25.7cm} ${k=2}$
\end{slide}

@@

\vspace{.5cm}
\centerline{\includegraphics[scale=3.3]{bijection}}

@@

\theo{Q1a}{Is the wiggly flip graph Hamiltonian?

@@

\theo{Q1b}{What is the diameter of the wiggly flip graph?

@@

\begin{slide}{Open problem 2: wiggly pseudotriangulations and duality}
%\hspace{1.6cm} Triangulations \hspace{3.4cm} Pseudotriangulations \hspace{2.5cm} Multitriangulations\\
%\vspace{-.5cm}\\

\vspace*{-.8cm}
\hspace*{-.6cm}\includegraphics[scale=1.9]{geometricStructures7}
\vspace{-10.5cm} \\ \hspace*{25.7cm} ${k=2}$

\vspace{7.8cm}
\theo{Q2}{Is there a dual interpretation of wiggly pseudotriangulations?}

\vspace*{-3cm}
\end{slide}

\begin{slide}{Open problem 3: wiggly pseudotriangulations of point sets}

@@

\vspace*{-15cm}
\begin{minipage}{13cm}
\theo{Q3a}{Is~$\wigglyComplex_{\b{P}}$ the boundary complex of a simplicial polytope?

@@

\vspace{1cm}
\theo{Q3b}{Is the graph of~$\wigglyComplex_{\b{P}}$ Hamiltonian?}

@@

\newpage

\vspace*{2cm}
\centerline{\includegraphics[scale=1.8]{wigglyFlipGraph}\quad\raisebox{.5cm}{\includegraphics[scale=1.8]{wigglyLattice}}}

\vspace*{.2cm}
\centerline{\includegraphics[scale=4]{wigglyThankYou}}
